### 2018-08-25 results.tex
Resolve issue #14
Figure 16 caption fixed #16

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials. Thus, a significant amount fissile material will be needed to make the reactor critical. 
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\end{figure}

@@

The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively. The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation. The confidence interval $\pm\sigma	$ is shaded.}
  \label{fig:fp_removal}
\end{figure}

>>>>

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials. 
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\end{figure}

@@

The effective multiplication factor of the core reduces gradually over operation time because the fissile material ($^{233}$U) continuously depletes from the fuel salt due to fission and, at the same time, fission products accumulates in the fuel salt.	Eventually, without fission products removal, the reactivity decreases to the subcritical state after approximately 500 and 1300 days of operation for cases with no removal and volatile gases \& noble metals removal, respectively. The time when the simulated core reaches subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. Therefore, removing fission products provides with significant neutronic benefit because allows achieve longer core lifetime.
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} model with removal of different fission product groups over 10 years of operation.}
  \label{fig:fp_removal}
\end{figure}
